---
title: "Exploratory Analysis"
author: "Josh Browning"
date: "October 11, 2015"
output: html_document
---

Load the libraries and the Mio Affitto dataset:

```{r}
suppressMessages({
library(data.table)
library(ggplot2)
library(scales)
library(glmnet)
library(sqldf)
library(reshape2)
library(romeHousePrices)
})

assignDirectory()

load(paste0(savingDir, "/detail_Mio_2015.10.05.06.28.32_cleaned.RData"))

## When filtering to top zones, quartieres, etc. how many should be kept?
maxToPlot = 10
```

Set some options:

```{r}
## Keep data.table from printing all the time
assign("depthtrigger", 100, data.table:::.global)
```

## Prezzo vs. Superficie

```{r, fig=TRUE}
d[, roundSuper := round(superficie/25) * 25]
print(ggplot(d, aes(x = prezzo, fill = factor(roundSuper))) +
    geom_bar(position = "fill") +
    xlim(c(0,3001)) + labs(y = "", fill = "superficio") +
    scale_y_continuous(labels = percent))
```


## Exploring the model

### Locali

Not surprisingly, price increases with number of rooms.  However, it's interesting to see that the increase seems to be faster than linear: prices really jump after 4 or 5 rooms.  But, that may just mean that we've moved into a group of really nice houses, whereas the 1-4 locali houses are a mix of fancy and not so fancy. 

```{r, fig = TRUE}
ggplot(d, aes(x = locali, y = prezzo)) +
    geom_point() + geom_smooth()
```

```{r, fig = TRUE}
ggplot(d, aes(x = locali, y = prezzo, group = locali)) +
    geom_boxplot()
```

### Superficie

```{r, fig = TRUE}
ggplot(d, aes(x = superficie, y = prezzo)) +
    geom_point() + geom_smooth()
```

```{r, fig = TRUE}
ggplot(d, aes(x = superficie, y = prezzo / superficie)) +
    geom_point() + geom_smooth()
```

### Bagni

```{r, fig = TRUE}
ggplot(d, aes(x = bagni, y = prezzo)) +
    geom_point()
```

```{r, fig = TRUE}
ggplot(d, aes(x = bagni, y = prezzo, group = bagni)) +
    geom_boxplot()
```

### Piano

### Zona

```{r, fig = TRUE}
d[, zonaCnt := .N, by = zona]
cutoff = sort(unique(d$zonaCnt), decreasing = TRUE)[maxToPlot]
ggplot(d[zonaCnt >= cutoff, ], aes(x = substr(zona, 1, 30), y = prezzo,
                                   group = zona)) +
    geom_boxplot() + theme(axis.text.x = element_text(angle = 90))
d[, zonaCnt := NULL]
```

### Quartiere

```{r, fig = TRUE}
d[, quartiereCnt := .N, by = quartiere]
cutoff = sort(unique(d$quartiereCnt), decreasing = TRUE)[maxToPlot]
ggplot(d[quartiereCnt >= cutoff, ], aes(x = quartiere, y = prezzo, group = quartiere)) +
    geom_boxplot() + theme(axis.text.x = element_text(angle = 90))
d[, quartiereCnt := NULL]
```


### CAP

```{r, fig = TRUE}
d[, capCnt := .N, by = CAP]
cutoff = sort(unique(d$capCnt), decreasing = TRUE)[maxToPlot]
ggplot(d[capCnt >= cutoff, ], aes(x = CAP, y = prezzo, group = CAP)) +
    geom_boxplot() + theme(axis.text.x = element_text(angle = 90))
d[, capCnt := NULL]
```

## Results of Model

- Prediction
- Residuals (look for trends)
- Best and worst deals

## Time series

- Average price over time: ggplot with many curves
- Average price over time: spatially with many images to capture time component
- One spatial plot indicating the percent change in house prices over some time period by region.

Partition data by
- CAP
- Zona
- Quartiere

## Simple spatial plots

- Price density
- Number of houses in region
- Number and/or quality of services in region
- Covariates (average superficie, average numeri di bagni/locali, ...)